Report

### 2021-01-19 report.Rmd
prediction plot and anova table works

```{r, eval = TRUE}
#https://stackoverflow.com/questions/44457243/regression-tables-in-r-markdown-rmarkdown-html-pdf
loadd(model_log_bm_f3y_table_medium)
model_log_bm_f3y_table_medium[["reg_table"]] %>% 
  filter(variable %in% get_com_str_var(all = FALSE)) %>%
  kable(.,
    booktabs = TRUE, 
    caption = 
      paste0(
      "Regression table for the model: dN =",
      "dB + B + dB*B + Inc*B + dB*Inc*B."
    )) %>% 
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
model_log_bm_f3y_table_medium[["anova_table"]] %>% 
  filter(variable %in% get_com_str_var(all = FALSE)) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA table for the model: dN =",
      "dB + B + dB*B + Inc*B + dB*Inc*B."
    )
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

@@

```{r}
loadd(pred_plot_signif)
pred_plot_signif_com <- pred_plot_signif %>%
  filter(variable %in% c(get_com_str_var(), "ct_ff"))
legend_signif <- get_legend(
  pred_plot_signif_com$myplot[[1]] +
    theme(legend.position = "bottom")
)
pred_plot_signif_com$myplot %<>% map(., ~.x + theme(legend.position = "none"))
top <- plot_grid(
  plotlist = pred_plot_signif_com$myplot,
  labels = pred_plot_signif_com$variable
)
plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
```

@@

```{r}
model_log_bm_f3y_table_medium[["anova_table"]] %>% 
  filter(!variable %in% get_com_str_var(all = FALSE)) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA table for the model: dN =",
      "dB + B + dB*B + Inc*B + dB*Inc*B."
    )
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")

```{r pred-other-com, fig.dim = c(12, 10)}
plot_signif <- pred_plot_signif %>%
  filter(!variable %in% get_com_str_var())
legend_signif <- get_legend(
  plot_signif$myplot[[1]] +
    theme(legend.position = "bottom")
)
plot_signif$myplot %<>% map(., ~.x + theme(legend.position = "none"))
top_signif_other <- plot_grid(
  plotlist = plot_signif$myplot,
  labels = plot_signif$variable
)
plot_grid(top_signif_other, legend_signif, nrow = 2, rel_heights = c(1, .1))
```

@@

@@

- Station ploted: `r st_network_to_plot`

>>>>

```{r, eval = TRUE}
#https://stackoverflow.com/questions/44457243/regression-tables-in-r-markdown-rmarkdown-html-pdf
#loadd(model_log_bm_f3y_table_medium)
#model_log_bm_f3y_table_medium[["reg_table"]] %>% 
  #filter(y %in% get_com_str_var(all = FALSE)) %>%
  #kable(.,
    #booktabs = TRUE, 
    #caption = 
      #paste0(
      #"Regression table for the model: dN =",
      #"dB + B + dB*B + Inc*B + dB*Inc*B."
    #)) %>% 
  #kable_styling(latex_options =c("scale_down", "stripped")) %>%
  #collapse_rows(columns = 1, valign = "top")
```

```{r}
#model_log_bm_f3y_table_medium[["anova_table"]] %>% 
  #filter(variable %in% get_com_str_var(all = FALSE)) %>%
  #kable(., booktabs = TRUE,
    #caption = 
      #paste0(
      #"ANOVA table for the model: dN =",
      #"dB + B + dB*B + Inc*B + dB*Inc*B."
    #)
  #) %>%
  #kable_styling(latex_options =c("scale_down", "stripped")) %>%
  #collapse_rows(columns = 1, valign = "top")
```

@@

```{r}
loadd(predict_plot)
pred_plot_signif_com <- predict_plot %>%
  filter(
    y %in% c(get_com_str_var(), "ct_ff", "log_rich_std"),
    x == "log_bm_std"
  )
legend_signif <- get_legend(
  pred_plot_signif_com$pred_plot[[1]] +
    theme(legend.position = "bottom")
)
pred_plot_signif_com$pred_plot %<>% map(., ~.x + theme(legend.position = "none"))
top <- plot_grid(
  plotlist = pred_plot_signif_com$pred_plot,
  labels = pred_plot_signif_com$y, nrow = 1
)
pred_plot1 <- plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
```

```{r}
pred_plot_rich <- predict_plot %>%
  filter( y %in% c(get_com_str_var(), "ct_ff"), x == "log_rich_std") %>%
  filter(!y %in% "rich_std")
legend_signif <- get_legend(
  pred_plot_rich$pred_plot[[1]] +
    theme(legend.position = "bottom")
)
pred_plot_rich$pred_plot %<>% map(., ~.x + theme(legend.position = "none"))
top <- plot_grid(
  plotlist = pred_plot_rich$pred_plot,
  labels = pred_plot_rich$y
)
pred_plot2 <- plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
```

```{r}
pred_plot_other <- predict_plot %>%
  filter( y %in% c("ct_ff", "w_trph_lvl_avg"), x == c("ct_ff", "w_trph_lvl_avg"))
legend_signif <- get_legend(
  pred_plot_other$pred_plot[[1]] +
    theme(legend.position = "bottom")
)
pred_plot_other$pred_plot %<>% map(., ~.x + theme(legend.position = "none"))
top <- plot_grid(
  plotlist = pred_plot_other$pred_plot,
  labels = pred_plot_other$y
)
pred_plot3 <- plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
```

```{r, fig.dim = c(12, 8)}
plot_grid(
  pred_plot1, plot_grid(pred_plot2, pred_plot3, ncol = 2),
  nrow = 2

)
```

```{r}
loadd(model_log_bm_f3y_table_medium)
model_log_bm_f3y_table_medium[["anova_table"]] %>%
  filter( y %in% c(get_com_str_var(), "ct_ff", "log_rich_std")) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA table for the model: dN =",
      "dB + B + dB*B + Inc*B + dB*Inc*B."
    )
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

@@

```{r pred-other-com, fig.dim = c(12, 10)}
pred_plot_signif <- predict_plot %>%
  filter(!y %in% c(get_com_str_var(), "ct_ff"), x == "log_bm_std")
legend_signif2 <- get_legend(
  pred_plot_signif_com$pred_plot[[1]] + theme(legend.position = "bottom")
)
pred_plot_signif$pred_plot %<>% map(., ~.x + theme(legend.position = "none"))
top2 <- plot_grid(
  plotlist = pred_plot_signif$pred_plot,
  labels = pred_plot_signif$y
)
plot_grid(top2, legend_signif2, nrow = 2, rel_heights = c(1, .1))
```

```{r}
model_log_bm_f3y_table_medium[["anova_table"]] %>% 
  filter(!y %in% get_com_str_var(all = FALSE)) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA table for the model: dN =",
      "dB + B + dB*B + Inc*B + dB*Inc*B."
    )
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

@@

```{r setup,  eval = TRUE}
knitr::opts_chunk$set(eval=FALSE)
```

@@

- Station ploted: `r #st_network_to_plot`
